### 2018-07-13 submission/manuscript.Rmd
update figure legends

**Figure 3: The number and range of OTUs in mock and fecal samples varies by polymerase.** The points represent the median number of OTUs for the mock samples. The lines represent the range of the minimum and maximum number of OTUs detected within the four fecal samples. The dotted black line represents the number of OTUs detected when only the references sequences for the mock community are clustered. A) The range in the number of OTUs detected in the mock samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases. B) The range in the number of OTUs detected in the different fecal samples increased as cycle number increased. This increased range also was larger for specific HiFi DNA polymerases.

**Figure 4: Lower five-cycle intervals have larger differences than higher five-cycle intervals using Bray-Curtis.** A) Within replicate difference based on the next 5-cycle PCR interval in mock samples. B) Within person differences based on the next 5-cycle PCR interval in fecal samples. The points represent the median Bray-Curtis index for the samples. The lines represent the range of the minimum and maximum Bray-Curtis index value for each PCR 5-cycle increment comparison. The closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar the bacterial community is of the two compared number of cycles.

**Figure 5: Biological variation in bacterial community composition due to individual was larger than number of cycles and polymerase used.** A) Using 16S rRNA gene sequencing, the classification of individuals was higher than any other model tested. The lines represent the median probability of correct classification and the gray points represent the individual probability from one run out of the 100 10-fold CV runs. B) The most important OTUs to the model classifying individuals are not the same as those that are most important for the number of cycles or polymerase used.

>>>>

**Figure 3: Subtle differences  based on number of cycles and polymerase used are detected in bacterial community composition of mock samples.** A) The range in the number of OTUs detected in the mock samples increased as cycle number increased. This range was larger for specific HiFi DNA polymerases. The points represent the median number of OTUs and the lines represent the range from the minimum to maximum number of OTUs detected within the four technical replicates. The dotted black line represents the number of OTUs detected when only the references sequences for the mock community are clustered. A) Within replicate difference based on the next 5-cycle PCR interval in mock samples. The lines represent the range of the minimum and maximum Bray-Curtis index value for each PCR 5-cycle increment comparison. The closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar the bacterial community is of the two compared number of cycles.

**Figure 4: Subtle differences based on number of cycles and polymerase used are detected in bacterial community composition of fecal samples.** A) The range in the number of OTUs detected in the different fecal samples increased as cycle number increased. This range was larger for specific HiFi DNA polymerases. The points represent the median number of OTUs and the lines represent the range from the minimum to maximum number of OTUs detected within the four fecal samples. B) Within person differences based on the next 5-cycle PCR interval in fecal samples. The points represent the median Bray-Curtis index for the samples. The lines represent the range of the minimum and maximum Bray-Curtis index value for each PCR 5-cycle increment comparison. The closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar the bacterial community is of the two compared number of cycles.

**Figure 5: Important OTUs for the number of cycles and polymerase models are not the most important OTUs in the model classifying individuals.** Color highlights the top 10 OTUs in number of cycles and polymerase used and where they fall in the model used to classify individuals. The majority of these top 10 OTUs have 0 importance to the model used to classify individuals.

### 2018-07-13 submission/manuscript.tex
update figure legends

\textbf{Figure 3: The number and range of OTUs in mock and fecal samples
varies by polymerase.} The points represent the median number of OTUs
for the mock samples. The lines represent the range of the minimum and
maximum number of OTUs detected within the four fecal samples. The
dotted black line represents the number of OTUs detected when only the
references sequences for the mock community are clustered. A) The range
in the number of OTUs detected in the mock samples increased as cycle
number increased. This range was also larger for specific HiFi DNA
polymerases. B) The range in the number of OTUs detected in the
different fecal samples increased as cycle number increased. This
increased range also was larger for specific HiFi DNA polymerases.

\textbf{Figure 4: Lower five-cycle intervals have larger differences
than higher five-cycle intervals using Bray-Curtis.} A) Within replicate
difference based on the next 5-cycle PCR interval in mock samples. B)
Within person differences based on the next 5-cycle PCR interval in
fecal samples. The points represent the median Bray-Curtis index for the
samples. The lines represent the range of the minimum and maximum
Bray-Curtis index value for each PCR 5-cycle increment comparison. The
closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar
the bacterial community is of the two compared number of cycles.

\textbf{Figure 5: Biological variation in bacterial community
composition due to individual was larger than number of cycles and
polymerase used.} A) Using 16S rRNA gene sequencing, the classification
of individuals was higher than any other model tested. The lines
represent the median probability of correct classification and the gray
points represent the individual probability from one run out of the 100
10-fold CV runs. B) The most important OTUs to the model classifying
individuals are not the same as those that are most important for the
number of cycles or polymerase used.

>>>>

\textbf{Figure 3: Subtle differences based on number of cycles and
polymerase used are detected in bacterial community composition of mock
samples.} A) The range in the number of OTUs detected in the mock
samples increased as cycle number increased. This range was larger for
specific HiFi DNA polymerases. The points represent the median number of
OTUs and the lines represent the range from the minimum to maximum
number of OTUs detected within the four technical replicates. The dotted
black line represents the number of OTUs detected when only the
references sequences for the mock community are clustered. A) Within
replicate difference based on the next 5-cycle PCR interval in mock
samples. The lines represent the range of the minimum and maximum
Bray-Curtis index value for each PCR 5-cycle increment comparison. The
closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar
the bacterial community is of the two compared number of cycles.

\textbf{Figure 4: Subtle differences based on number of cycles and
polymerase used are detected in bacterial community composition of fecal
samples.} A) The range in the number of OTUs detected in the different
fecal samples increased as cycle number increased. This range was larger
for specific HiFi DNA polymerases. The points represent the median
number of OTUs and the lines represent the range from the minimum to
maximum number of OTUs detected within the four fecal samples. B) Within
person differences based on the next 5-cycle PCR interval in fecal
samples. The points represent the median Bray-Curtis index for the
samples. The lines represent the range of the minimum and maximum
Bray-Curtis index value for each PCR 5-cycle increment comparison. The
closer a sample is to a Bray-Curtis index of 1.00 the more dissimilar
the bacterial community is of the two compared number of cycles.

\textbf{Figure 5: Important OTUs for the number of cycles and polymerase
models are not the most important OTUs in the model classifying
individuals.} Color highlights the top 10 OTUs in number of cycles and
polymerase used and where they fall in the model used to classify
individuals. The majority of these top 10 OTUs have 0 importance to the
model used to classify individuals.
